---
title: "Workflow, Wrangle(Intro), & Tibbles"
subtitle: "R4DS book club"
author: "Meenakshi Kushwaha"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class:center, middle, inverse

#Workflow
## R Projects
---

---
class:center, middle, inverse
#Tibbles
---
#What are Tibbles
- Data frames with different features to make life easier
---
# How to create tibbles

.pull-left[
Using `as_tibble()`
```{r}
library(tidyverse)
as_tibble(cars)
```

]

--

.pull-right[
From individual vectors
```{r}
tibble(
  x = 1:5, 
  y = 1, 
  z = x ^ 2 + y
)
```

]
---
# How to create tibbles


.pull-left[
Using **non-syntactic** names
```{r}
tb <- tibble(
  `:)` = "smile", 
  ` ` = "space",
  `2000` = "number"
)
tb
```

]

--
.pull-right[
Using tribble(), short for **tr**ansposed tibble
```{r}
tribble(
  ~x, ~y, ~z,
  #--|--|----
  "a", 2, 3.6,
  "b", 1, 8.5
)
```
]
---
#Tibble vs Data Frames - Printing
Tibble shows only the first 10 rows, and all the columns that fit on screen
```{r}
as_tibble(nycflights13::flights)
```
---
#Tibble vs Data Frames - Subsetting
- Extract by name
```{r}
cars$speed
```


- Extract by position
  - `cars[[1]]`

- Using in pipe
  - `cars %>% .x$speed`
  - `cars %>% .x[[1]]`

*Tibbles are stricter than dataframes : they never do partial matching*